Gap formation and stability in non-isothermal protoplanetary discs

### 2014-09-11 paper/paper.tex
started intro

\section{Introduction}\label{intro}

>>>>

\section{Introduction}\label{intro}
{
\bf 
observational motivation: asymmetric dust distributions. 
theoretical motivations: generalize gap stability to include energy equation. 
}

Disk-planet interaction plays an important role in the theory of planet formation and has been invoked to explain 
sub-structures obsererved in transition disks. It is well-known that a sufficiently massive planet opens a disk gap, and
such structures have been detected. A more recent theoretical result is that planetary gaps are dynamically unstable under
certain conditions. The so-called Rossby wave instability operates in radially structured disks, and leads 
to vortex-formation.

In this work, we extend the study of planetary gap stability against vortex formation to non-isothermal discs. 
We include a fluid energy equation in the hydrodynamical equations describing disk-planet systems. We consider a simple
cooling function and examine the effect cooling rate on the stability of planetary gaps.

This paper is organised as follows.
